Impact of IPTp Regimen on Pregnancy Outcomes in a Malaria-Endemic Setting

### 2025-04-24 products/manuscript/Manuscript.qmd
Images2

@@

**Table 5: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  here::here("Images", "Adjusted ratio   less 25 Years.png")
)

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  here::here("Images", "Figure 3. Predicted Probability.png")
)

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# 1) Load here() before you call i_am()
library(here)

# 2) Tell here() where this document lives, relative to the project root.
#    (Your project root is "Joseph-MADA-project", so we point to "products/manuscript/Manuscript.qmd")
here::i_am("products/manuscript/Manuscript.qmd")

# 3) (Optional) now load knitr and set the knit root to the project root
library(knitr)
opts_knit$set(root.dir = here::here())

@@

**Table 5: Adjusted Odds Ratios for Adverse Birth Outcomes Among Young Pregnant Women (<25 Years)**

```{r fig-adjusted-u25, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  normalizePath(
    here::here("Images", "AdjustedRatio.png"),
    winslash = "/"
  )
)

@@

**Figure 3: Predicted Probability of Adverse Outcome by Gravidity (Age < 25)**
```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::include_graphics(
  normalizePath(
    here::here("Images", "Figure 3. Predicted Probability.png"),
    winslash = "/"
  )
)
